### 2014-08-13 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Fix typo
Chicago Fire: update to chemical reaction

On November 2, 2012, a fire in a 2~\sfrac{1}{2}~story wood frame residential structure claimed the life of a captain of the Chicago Fire Department. NIST examined the fire dynamics of this incident at the request of NIOSH and the Chicago Fire Department. Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide}  software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire. The specific objectives of the simulations detailed in this report are: 
\begin{enumerate}
\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this multi-story residential structure using physics-based calculations.
\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Chicago Fire Department likely experienced during the course of their interior operations.
\end{enumerate}
This document describes the input and the results of the FDS (version 6.0.0) simulations. The simulations were developed using a combination of knowledge of the fire scenario and appropriate engineering approximations and assumptions. Analysis of the simulation results focuses on the hazardous conditions that developed following the development of a flow path inside of the structure. This document is organized as follows: Section~\ref{fire_sum} provides a summary of the fire incident, Section~\ref{model} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{results} presents the simulation results, and Section~\ref{discussion} discusses the simulation results as they relate to firefighter safety and effectiveness. Appendix~\ref{app_draw} contains dimensioned drawings of the first and second floor of the structure.

@@

Wood fuel can be represented by the chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with specified yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$) and soot ($y_{\mathrm{C}}=0.015 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}. The product yields are expressed in terms of the amount of carbon monoxide or soot emitted per unit mass of fuel consumed (kg/kg) and can be found in the Society of Fire Protection Engineers (SFPE) Handbook~\cite{SFPE:Tewarson}. A balanced chemical reaction for wood combustion can written as:

\begin{multline}
\C\H_{1.7}\O_{0.74}\N_{0.002} + 4.89(0.208\,\O_{2} + 0.783\,\N_{2} + 0.387\text{\sc{e}-}3\,\C\O_{2} + 0.834\text{\sc{e}-}2\,\H_{2}\O) \\ 
\rightarrow 5.84(0.719\text{\sc{e}-}3\,\C\O + 0.168\,\C\O_{2} + 0.155\,\H_{2}\O + 0.669\,\N_{2} + 0.693\text{\sc{e}-}2\,\C)
\label{eq:wood_comb}
\end{multline}

>>>>

On November 2, 2012, a fire in a 2~\sfrac{1}{2}~story wood frame residential structure claimed the life of a captain of the Chicago Fire Department. NIST examined the fire dynamics of this incident at the request of NIOSH and the Chicago Fire Department. Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide}  software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire. The specific objectives of the simulations detailed in this report are: 
\begin{enumerate}
\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this multi-story residential structure using physics-based calculations.
\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Chicago Fire Department likely experienced during the course of their interior operations.
\end{enumerate}
This document describes the input and the results of the FDS (version 6.1.1) simulations. The simulations were developed using a combination of knowledge of the fire scenario and appropriate engineering approximations and assumptions. Analysis of the simulation results focuses on the hazardous conditions that developed following the development of a flow path inside of the structure. This document is organized as follows: Section~\ref{fire_sum} provides a summary of the fire incident, Section~\ref{model} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{results} presents the simulation results, and Section~\ref{discussion} discusses the simulation results as they relate to firefighter safety and effectiveness. Appendix~\ref{app_draw} contains dimensioned drawings of the first and second floor of the structure.

@@

Wood fuel can be represented by the chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with specified yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$) and soot ($y_{\mathrm{C}}=0.015 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}. The product yields are expressed in terms of the amount of carbon monoxide or soot emitted per unit mass of fuel consumed (kg/kg) and can be found in the Society of Fire Protection Engineers (SFPE) Handbook~\cite{SFPE:Tewarson}. A balanced chemical reaction for wood combustion can be written as:

\begin{multline}
\C\H_{1.7}\O_{0.74}\N_{0.002} + 4.91(0.208\,\O_{2} + 0.783\,\N_{2} + 0.387\text{\sc{e}-}3\,\C\O_{2} + 0.834\text{\sc{e}-}2\,\H_{2}\O) \\ 
\rightarrow 5.74(0.636\text{\sc{e}-}3\,\C\O + 0.168\,\C\O_{2} + 0.155\,\H_{2}\O + 0.670\,\N_{2} + 0.613\text{\sc{e}-}2\,\C)
\label{eq:wood_comb}
\end{multline}
